Exploring the Impact of Atypical Events on Regret: Analysis Through Hitchhiker, Car Accident, and Robbery Scenarios

### 2024-02-14 outputs/paper/paper.qmd
almost final version

All of the data for REGRET and COMPENSATION contained 344 observations, and 21 VARIABLES were taken from the data underlying Kutscher and Feldman's study[@kutscher2019impact], which was collected as a questionnaire. The questionnaire recipients read a scenario in which a robbery occurred at a grocery store. In the first scenario (routine behaviour), Mr. Paul visited the store he frequented. In the second scenario (self-produced exception), the main character went to another store because he wanted a change of scenery. In the third scenario (other produced exception), Mr. Paul is forced to patronize another store because the store he frequents is closed for construction, and he runs into a robbery taking place in the store. In the next question, we ran a compensation measure followed by a regret measure. Respondents were asked how much money Mr. Paul should receive in compensation for his loss—scale from 0 to 10: 0\$ to 1000000\$. The next question was: assume no compensation was given to Mr. Paul. How much regret does he feel over the situation? Scale 1 from no regret to 5, very strong regret.

@@

## fig1

```{r echo=FALSE, message=FALSE, fig.cap="Proportions for perceived regret, injunctive social norms, descriptive social norms, and negative affect", label= "fig-1"}
fig1_data <- data.frame(
  Scenario = c("Smith - Routine", "Jones - Exception"),
  PerceivedRegret = c(7.9, 92.1),
  InjunctiveSocialNorms = c(4.7, 95.3),
  DescriptiveSocialNorms = c(90.6, 9.4),
  NegativeAffect = c(7.3, 92.7)
)

@@

## fig2

>>>>

All of the data for REGRET and COMPENSATION contained 344 observations, and 21 VARIABLES were taken from the data underlying Kutscher and Feldman's study[@kutscher2019impact], which was collected as a questionnaire. The questionnaire recipients read a scenario in which a robbery occurred at a grocery store. In the first scenario (routine behaviour), Mr. Paul visited the store he frequented. In the second scenario (self-produced exception), the main character went to another store because he wanted a change of scenery. In the third scenario (other produced exception), Mr. Paul is forced to patronize another store because the store he frequents is closed for construction, and he runs into a robbery taking place in the store. In the next question, we ran a compensation measure followed by a regret measure. Respondents were asked how much money Mr. Paul should receive in compensation for his loss—scale from 0 to 10: 0 dollar to 1000000 dollar. The next question was: assume no compensation was given to Mr. Paul. How much regret does he feel over the situation? Scale 1 from no regret to 5, very strong regret.

@@

## Exploring Social Norms and Personal Reactions from the Perspective of Behavior and Emotions
```{r echo=FALSE, message=FALSE, fig.cap="Proportions for perceived regret, injunctive social norms, descriptive social norms, and negative affect", label= "fig-1"}
fig1_data <- data.frame(
  Scenario = c("Smith - Routine", "Jones - Exception"),
  PerceivedRegret = c(7.9, 92.1),
  InjunctiveSocialNorms = c(4.7, 95.3),
  DescriptiveSocialNorms = c(90.6, 9.4),
  NegativeAffect = c(7.3, 92.7)
)

@@

## Comparative Analysis of Perceived Regret and Luck Between Routine and Exception Circumstances
